\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
paper updates
verslag

For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
\\ \\
\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct}

@@

\subsubsection{Replacing the twins}
Similar to 4.1

@@

\end{multicols}
\begin{appendices}

\section{Python code}
\lstset{language=Python}
\begin{lstlisting}[label={gettwins}]
def gettwins(g):
    nbs = []
    nbs2 = []
    for vertex in g.V():
        nb = vertex.nbs()[:]
        nb.sort(key=lambda x: x._label)
        nbs.append(tuple(nb))
        nb.append(vertex)
        nb.sort(key=lambda x: x._label)
        nbs2.append(tuple(nb))
    falsetwins = {}
    for i, item in enumerate(nbs):
        if item in falsetwins.keys():
            falsetwins[item].append(g.V()[i])
        else:
            falsetwins[item] = [g.V()[i]]
    twins = {}
    for i, item in enumerate(nbs2):
        if item in twins.keys():
            twins[item].append(g.V()[i])
        else:
            twins[item] = [g.V()[i]]
    falsetwins = {k: v for k, v in falsetwins.items() if len(v) > 1}
    twins = {k: v for k, v in twins.items() if len(v) > 1}
    return list(falsetwins.values()), list(twins.values()), list(falsetwins.keys()), list(twins.keys())   
\end{lstlisting}
\end{appendices}

>>>>

For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.

@@

\subsubsection{Replacing the twins}
The algorithm \emph{preprocessing} can be found in appendix \ref{preprocessing}. In line 2 the twins and falsetwins are defined and if there are none the program will terminate. If there are any twins all edges with a head or tail in one of these twins will be deleted. The complexity of this is $O(m +$ number of vertices (\emph{twins}+\emph{falsetwins}))$ < O (nm)$. Then in line 13-19 all vertices which are in twins or falsetwins will be removed. The complexity of this is $O(n^2)$. In line 20-28 a new colored vertex will be added for each (false) twin $(O(n)$ and finnaly the edges from these vertices will be added ($O(n^2 (n+m)$). The worst case complexity of this algorithm is ($O(n^2 (n+m)$), however in average there are much less (false) twins than vertices (there are at most $n/2$). These twins also have much less than $n$ neighbours.

@@

\end{multicols}
\newpage
\begin{appendices}

\section{Python code}
\lstset{language=Python}
\begin{lstlisting}[label={gettwins}]
def gettwins(g):
    nbs = []
    nbs2 = []
    for vertex in g.V():
        nb = vertex.nbs()[:]
        nb.sort(key=lambda x: x._label)
        nbs.append(tuple(nb))
        nb.append(vertex)
        nb.sort(key=lambda x: x._label)
        nbs2.append(tuple(nb))
    falsetwins = {}
    for i, item in enumerate(nbs):
        if item in falsetwins.keys():
            falsetwins[item].append(g.V()[i])
        else:
            falsetwins[item] = [g.V()[i]]
    twins = {}
    for i, item in enumerate(nbs2):
        if item in twins.keys():
            twins[item].append(g.V()[i])
        else:
            twins[item] = [g.V()[i]]
    falsetwins = {k: v for k, v in falsetwins.items() if len(v) > 1}
    twins = {k: v for k, v in twins.items() if len(v) > 1}
    return list(falsetwins.values()), list(twins.values()), list(falsetwins.keys()), list(twins.keys())   
\end{lstlisting}

\begin{lstlisting}[label={preprocessing}]
def preprocessing(g):
	falsetwins, twins, falsetwinsN, twinsN = gettwins(g)
	lftwins = len(falsetwins)
	ltwins = len(twins)
	if lftwins != 0 or ltwins != 0:
		deledges = []
		for i, e in enumerate(g._E):
			if any(e._tail in ftwin for ftwin in falsetwins) or any(e._head in ftwin for ftwin in falsetwins) or any(e._tail in twin for twin in twins) or any(e._head in twin for twin in twins):
				deledges.append(i)
		deledges.sort(reverse=True)
		for i in deledges:
			g._E.pop(i)
		delnodes = []
		for i, V in enumerate(g._V):
			if any(V in ftwin for ftwin in falsetwins) or any(V in twin for twin in twins):
				delnodes.append(i)
		delnodes.sort(reverse=True)
		for i in delnodes:
			g._V.pop(i)
		combined = falsetwinsN + twinsN
		mx = 0
		for i, twin in enumerate(falsetwins):
			g.addvertexobject(twin[0], True, len(twin))
			twin[0].colornum = -twin[0].twinsize
			mx = max(mx, len(twin))
		for i, twin in enumerate(twins):
			g.addvertexobject(twin[0], True, len(twin) + mx)
			twin[0].colornum = -twin[0].twinsize - mx
		for i, twin in enumerate(falsetwins + twins):
			for j in combined[i]:
				if j in g.V() and twin[0] != j and not g.findedge(twin[0],k)
					g.addedge(twin[0], j)
		g._V.sort(key=lambda x: x._label)
	return g, lftwins, ltwins
\end{lstlisting}

\end{appendices}
